\jaxcosmo: An End-to-End Differentiable and GPU Accelerated Cosmology Library

### 2023-01-11 paper_OJA.tex
Add author D. Kirkby
Add author contribution

\author{
J.~E. Campagne$^{1,\ast}$, 
F. Lanusse$^2$, 
J. Zuntz$^3$,\\
\jaxcosmo\ contributors}
\thanks{$^\ast$jean-eric.campagne@ijclab.in2p3.fr}

\affiliation{$^1$Université Paris-Saclay, CNRS/IN2P3, IJCLab, 91405 Orsay, France}

@@

%%%
\section*{CRedit authorship contribution statement}
\textbf{J.E Campagne:} Conceptualization, Methodology, Software, Validation, Writing, Visualization.
\textbf{F. Lanusse:}, Conceptualization, Methodology, Software, Validation, Writing, Project administration \textbf{J. Zuntz:} Investigation, Writing.

>>>>

\author{
J.~E. Campagne$^{1,\ast}$, 
F. Lanusse$^2$, 
J. Zuntz$^3$,
A. Peel$^4$\\
\jaxcosmo\ contributors}
\thanks{$^\ast$jean-eric.campagne@ijclab.in2p3.fr}

\affiliation{
$^1$Université Paris-Saclay, CNRS/IN2P3, IJCLab, 91405 Orsay, France\\
$^4$Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, Switzerland}

@@

%%%
\section*{CRedit authorship contribution statement}
\textbf{J.E Campagne:} Conceptualization, Methodology, Software, Validation, Writing, Visualization.
\textbf{F. Lanusse:}, Conceptualization, Methodology, Software, Validation, Writing, Project administration.
\textbf{J. Zuntz:} Investigation, Writing.
\textbf{A. Peel:} Software, Validation.
